EP1162_Prelim_Data_Screening

### 2020-03-02 data-raw/ep1162_prelimDataScreening.Rmd
Data cleaning

@@

```{r}
dat %>% 
  write.csv(file=here::here("data-raw","ep1162_finalDataCheck.csv"))

dat %>% 
  save(file=here::here("data","ep1162_Data.RData")

>>>>

### Remove trees with DBH<7.5cm DBH for that year
We need to remove trees from the record that have less than 7.5cm DBH recorded.

There are `dat %>% filter(DBH<7.5) %>% nrow()` records of trees with less than 7.5cm DBH that will be removed using the following chunk.

dat<- # re-assign to dat
  dat %>% 
  filter(DBH>=7.5) # keep trees >= 7.5cm DBH

@@

```{r}
dat %>% 
  write.csv(file=here::here("data-raw","ep1162_finalData.csv"),
            row.names=F,
            na="")

dat %>% 
  save(file=here::here("data","ep1162_Data.RData"))
